### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@ef77f3cb7cf4bb330d492cab4e350c00a27950b3 🚀

\[
\mathbf{M} = \begin{pmatrix}
    \rho^2 & \rho (1-\rho) \\
    (1-\rho) \rho & (1-\rho)^2
\end{pmatrix}
\]

\hypertarget{numerical-experiments}{%
\section{Numerical experiments}\label{numerical-experiments}}

>>>>

\[
\mathbf{M} = \begin{pmatrix}
    \rho^2 & \rho (1-\rho) \\
    (1-\rho) \rho & (1-\rho)^2
\end{pmatrix} \,.
\]

In order to regulate the skill of this classifier, we can define a skill
matrix \(\mathbf{S}\) with diagonal elements equal to \(s\), and
off-diagonal elements equal to \((1-s)\), and re-express the
skill-adjusted confusion matrix as \(\mathbf{M} \odot \mathbf{S}\),
\emph{i.e.}

\[
\begin{pmatrix}
    \rho^2 & \rho (1-\rho) \\
    (1-\rho) \rho & (1-\rho)^2
\end{pmatrix} \odot \begin{pmatrix}
    s & (1-s) \\
    (1-s) & s
\end{pmatrix}
\]

Note that when \(s=0\), \(\mathbf{Tr}(\mathbf{M}) = 0\) (the classifier
is \emph{always} wrong), when \(s=0.5\), the classifier is no-skill and
guesses at random, and when \(s=1\), the classifier is perfect.

The second element we can adjust in this hypothetical classifier is its
bias, specifically its tendency to over-predict interactions. Like
above, we can do so by defining a bias matrix \# Numerical experiments
